Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-15 manuscript/manuscript.tex
Modifications to manuscript: added gxx and gyy notice

We approximated the spherical shell by a mesh of $30^\circ \times 30^\circ$ tesseroids and calculated the gravity potential, the vertical component of the gradient ($g_z$) and the $g_{zz}$ component of the Marussi tensor on four different grids: (1) a grid located at the pole, (2) another one on the Equator, (3) one located at satellite height and (4) a big grid of $30^\circ \times 30^\circ$.
More information about this grids can be found in the Table \ref{tab:grids}.

@@

The tests were only performed on these three magnitudes because the other components of the gravity gradient and Marussi tensor are equal to zero due to the rotational symmetries of the spherical shell. \todo{corregir esto, los elementos diagonales del tensor fueron testeados, pero no lo mostramos pq son muy similares al gzz}

@@

The tests were performed on a thin and a thick spherical shell of 1 km and 35 km of thickness, respectively.
The results for both cases can be seen in Figures \ref{fig:D-linear-thin} and \ref{fig:D-linear-thick}.

For the linear density case, we can observe that the calculation of the potential and the $g_z$ component of its gradient needs a value of $D=1$ and $D=2$, respectively, in order to ensure an accuracy of 0.1\%.
On the other hand, the $g_{zz}$ computations show a noticeable difference between the thin and the thick shell: the first one needs a value of $D=8$ while the later only a $D=3.5$.
We will keep the more conservative result of $D=8$ in case of computing the $g_{zz}$ tensor component in case of a linear density tesseroid.

@@

\noindent where $A$ = 1kg/m$^3$ and $b$ = 1000km.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively, and the results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.

@@

Because the constant $b$ controls the variation of the density function we wanted to test how does the accuracy of the method behaves at different values of $b$.
We computed the difference between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution on the big grid of 30$^\circ\times$30$^\circ$ (see Table \ref{tab:grids}).
For each value of $b$ we computed these difference for the same set of values of $D$ we've been using on the previous tests, obtaining one curve for each kind of variation.

>>>>

We approximated the spherical shell by a mesh of $30^\circ \times 30^\circ$ tesseroids and calculated the gravity potential, the vertical component of the gradient ($g_z$) and the diagonal components of the Marussi tensor ($g_{xx}$, $g_{yy}$, $g_{zz}$) on four different grids: (1) a grid located at the pole, (2) another one on the Equator, (3) one located at satellite height and (4) a big grid of $30^\circ \times 30^\circ$.
More information about this grids can be found in the Table \ref{tab:grids}.

@@

The tests were only performed on these magnitudes because the other components of the gravity gradient and Marussi tensor are equal to zero due to the rotational symmetries of the spherical shell.

@@

The tests were performed on a thin and a thick spherical shell of 1 km and 35 km of thickness, respectively.
In Figures \ref{fig:D-linear-thin} and \ref{fig:D-linear-thick} we can see the results for the potential, the vertical component of the gradient and the $g_{zz}$ component of the Marussi tensor.
Because the other two diagonal components of the tensor show similar results as the ones obtained for the $g_{zz}$, we exclude them from the figure.
Although they can be found in the repository. \todo{chequear}

For the linear density case, we can observe that the calculation of the potential and the $g_z$ component of its gradient needs a value of $D=1$ and $D=2$, respectively, in order to ensure an accuracy of 0.1\%.
On the other hand, the $g_{zz}$ computations show a noticeable difference between the thin and the thick shell: the first one needs a value of $D=8$ while the later only a $D=3.5$.
We will keep the more conservative result of $D=8$ in case of computing the Marussi tensor components in case of a linear density tesseroid.

@@

\noindent where $A$ = 1kg/m$^3$ and $b$ = 1000km.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively, and the results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.
Once again, the results for $g_{xx}$ and $g_{yy}$ are very similar to the ones obtained for $g_{zz}$, so we exclude them. Although, they can be found in the repository.

@@

Because the constant $b$ controls the variation of the density function we wanted to test how does the accuracy of the method behaves at different values of $b$.
We computed the difference between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution on the big grid of 30$^\circ\times$30$^\circ$ (see Table \ref{tab:grids}).
For each value of $b$ we calculated these difference for the same set of values of $D$ we've been using on the previous tests, obtaining one curve for each kind of variation.
